Figures

### 2025-08-16 code/07_data_analysis.Rmd
Added another sensitivity analysis without non-aromatic and aromatic comparison

pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs)

@@

intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR)
# saving the model
# saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))

# saving the dataset for this model
# write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
```

@@

# saving the model
# saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))

# saving the dataset for this model
# write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
```

@@

>>>>

pacman::p_load(here,tidyverse,metafor,ggpubr,orchaRd,ggpubfigs,readr)

@@

intercept_lnRR<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR)
# saving the model
 saveRDS(intercept_lnRR, file = here::here("model/intercept_lnRR.rds"))

# saving the dataset for this model
 write.csv(dataset_lnRR,here::here("data/04_data_analysis/intercept_lnRR.csv"))
```

@@

# saving the model
 saveRDS(intercept_SMDH, file = here::here("model/intercept_SMDH.rds"))

# saving the dataset for this model
 write.csv(dataset_SMDH,here::here("data/04_data_analysis/intercept_SMDH.csv"))
```

@@

# Sensitivity Analysis: Excluding Non-aromatic Vs. Aromatic

We are aware that removing over 50% of the dataset will cause some moderator levels to drop out. But if our goal is to critically examine the role of aromaticity and potentially argue that its importance has been overstated, this could be a very informative step.

## For the lnRR effect size...
dataset_lnRR_no_comp1<-dataset_lnRR%>%filter(comparision_type!=1 | is.na(comparision_type))
## Only some rows are removed... 
nrow(dataset_lnRR)-nrow(dataset_lnRR_no_comp1)

VCV_lnRR_no_comp1 <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_no_comp1,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

SA_lnRR_no_comp1<- rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_no_comp1, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_lnRR_no_comp1)

# Saving the model
saveRDS(SA_lnRR_no_comp1, file = here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))

# saving the dataset for this model
write.csv(dataset_lnRR_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_lnRR_no_comp1.csv"))

dataset_SMDH_no_comp1<-dataset_SMDH%>%filter(comparision_type!=1 | is.na(comparision_type))
## Only some rows are removed... 
nrow(dataset_SMDH)-nrow(dataset_SMDH_no_comp1)

VCV_SMDH_no_comp1 <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_no_comp1,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )

SA_SMDH_no_comp1<- rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_no_comp1, # specify lnRR's sampling variance-covariance matrix;
                    mods = ~ 1,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                    control = list(optimizer="optim"),
                    test = "t",
                    data = dataset_SMDH_no_comp1)

# Saving the model
saveRDS(SA_SMDH_no_comp1, file = here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))

# saving the dataset for this model
write.csv(dataset_SMDH_no_comp1,here::here("data/05_data_sensitivity_analysis/dataset_SMDH_no_comp1.csv"))

#----------------------------------------------------------------------------
# Rerunning the two mechanistic hypothesis meta-regressions with those effect sizes excluded
#----------------------------------------------------------------------------

lnRR_hypothesis_no_comp1 <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_no_comp1,# specify lnRR's sampling variance;
                    mods = ~ - 1 + Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_no_comp1)
# Save model
saveRDS(lnRR_hypothesis_no_comp1, file = here::here("model/lnRR_hypothesis_no_comp1.rds"))

SMDH_hypothesis_no_comp1 <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_no_comp1,# specify lnRR's sampling variance;
                    mods = ~ - 1 + Hypothesis,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_no_comp1)

# Save model
saveRDS(SMDH_hypothesis_no_comp1, file = here::here("model/SMDH_hypothesis_no_comp1.rds"))

#----------------------------------------------------------------------------
## Now re-running all the 5 meta-regressions once again
#----------------------------------------------------------------------------

# This analysis only includes dataset that has a proxy relating to comaparision type
dataset_lnRR_design_no_comp1 <- dataset_lnRR_no_comp1 %>% filter(!is.na(comparision_type))

VCV_lnRR_design_no_comp1 <- vcalc(vi = lnRR_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_lnRR_design_no_comp1,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
lnRR_design_no_comp1 <-
  metafor::rma.mv(yi = lnRR_sign, # specify lnRR as the effect size measure;
                    V = VCV_lnRR_design_no_comp1 ,# specify lnRR's sampling variance;
                    mods = ~ - 1 + comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_lnRR_design_no_comp1 )

# Saving the model
saveRDS(lnRR_design_no_comp1, file = here::here("model/lnRR_design_no_comp1.rds"))

# This analysis only includes dataset that has a proxy relating to comaparision type
dataset_SMDH_design_no_comp1 <- dataset_SMDH_no_comp1 %>% filter(!is.na(comparision_type))

VCV_SMDH_design_no_comp1 <- vcalc(vi = SMDH_variance,
                  cluster = paper_ID,
                  obs = Observation_ID,
                  data = dataset_SMDH_design_no_comp1,
                  rho = 0.5 # assuming that the effect sizes within the same study are correlated with rho = 0.5
                  )
SMDH_design_no_comp1 <-
  metafor::rma.mv(yi = SMDH_sign, # specify lnRR as the effect size measure;
                    V = VCV_SMDH_design_no_comp1 ,# specify lnRR's sampling variance;
                    mods = ~ - 1 + comparision_type,
                    random = list(~ 1 | paper_ID,
                                  ~ 1 | Observation_ID,
                                  ~ 1 | group_ID_coded,
                                  ~ 1 | population_ID,
                                  ~ 1 | bird_species),
                    method = "REML",
                  test = "t",
                  control = list(optimizer="optim"),
                  data = dataset_SMDH_design_no_comp1 )

# Saving the model
saveRDS(SMDH_design_no_comp1, file = here::here("model/SMDH_design_no_comp1.rds"))
```

### 2025-08-16 code/08_figures-tables.Rmd
Temp commit back to desktop
Added another sensitivity analysis without non-aromatic and aromatic comparison

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1.5,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

@@

lnRR_design_plot_cropped <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

SMDH_design_plot_cropped <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
   trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
    k.pos = c(1.9,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. Aromatic","No material\nVs. Aromatic", "No material\nVs. Non-Aromatic"))

@@

# -------- Supplementary Material Table ----------

@@

\

@@

@@

pacman::p_load(gt, tidyverse, metafor, purrr, stringr)

>>>>

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1.5,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))

@@

lnRR_design_plot_cropped <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))

SMDH_design_plot_cropped <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
   trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
    k.pos = c(1.9,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))

@@

# ----- Supplementary Material Table -------

@@

@@

## Table: RoB Meta-regressions

# Loading models for blinding performed or not
lnRR_blinding<-readRDS(here::here("model/lnRR_blinding.rds"))
SMDH_blinding<-readRDS(here::here("model/SMDH_blinding.rds"))

# Loading models for random sampling assignment performed or not
lnRR_random_assignment<-readRDS(here::here("model/lnRR_random_assignment.rds"))
SMDH_random_assignment<-readRDS(here::here("model/SMDH_random_assignment.rds"))

# Loading models for missing data present or not
lnRR_missing_data<-readRDS(here::here("model/lnRR_missing_data.rds"))
SMDH_missing_data<-readRDS(here::here("model/SMDH_missing_data.rds"))

```{r}
pacman::p_load(gt, tidyverse, metafor, purrr, stringr)

## For lnRR Values
lnRR_results_RoB <- extractor_metareg(lnRR_blinding,"blinding")%>%
  bind_rows(extractor_metareg(lnRR_random_assignment,"random_assignment"))%>%
  bind_rows(extractor_metareg(lnRR_missing_data,"missing_data"))%>%
  mutate(effect_size = "lnRR")

## For SMDH Values
SMDH_results_RoB <- extractor_metareg(SMDH_blinding,"blinding")%>%
  bind_rows(extractor_metareg(SMDH_random_assignment,"random_assignment"))%>%
  bind_rows(extractor_metareg(SMDH_missing_data,"missing_data"))%>%
  mutate(effect_size = "SMDH")

## Now let's write the table for publication:
# Combine both results
combined_results_RoB <- bind_rows(lnRR_results_RoB, SMDH_results_RoB)%>%
  pivot_wider(
    id_cols = c(moderator, level),
    names_from = effect_size,
    values_from = c(estimate, p_value, CI, PI, k, n),
    names_glue = "{.value}_{effect_size}"
  )%>% # Prepare row labels to mimic grouping
  arrange(moderator, level)%>%
  mutate(row_type = "level")

# Final combined table with headers and levels
 combined_results_RoB <- combined_results_RoB %>%
   # bind_rows(moderator_header ,combined_results) %>%
  arrange(moderator, row_type)%>% select(-row_type)%>%
  relocate(level, .after = moderator)%>%
  mutate(moderator = case_when(
    moderator == "blinding" ~ "1. Blinding",
    moderator == "random_assignment" ~ "2. Random assignment to treatment",
    moderator == "missing_data" ~ "3. Partial Reporting"
  ))%>%mutate(moderator = factor(
    moderator,
    levels = c(
      "1. Blinding",
      "2. Random assignment to treatment",
      "3. Partial Reporting"
    )
  ))%>%
  arrange(moderator)%>%
  mutate(level = case_when(level=="y" ~ "Yes",
                           level=="n" ~ "No", .default=level))

# Clean up or reorder columns for display
# Select and order columns for clarity
RoB_table <- combined_results_RoB %>%
  gt(groupname_col = "moderator") %>%
  tab_header(title = md("**Multilevel Meta Regressions for Risk of Bias**")) %>%
  cols_label(
    # R2_marginal_lnRR = "R²_mar",
    # R2_marginal_SMDH = "R²_mar",
    level = "Level",
    estimate_lnRR = "Estimate",
    CI_lnRR = "95% CI",
    PI_lnRR = "95% PI",
    p_value_lnRR = "P-val",
    k_lnRR = "k",
    n_lnRR = "n",
    estimate_SMDH = "Estimate",
    CI_SMDH = "95% CI",
    PI_SMDH = "95% PI",
    p_value_SMDH = "P-val",
    k_SMDH = "k",
    n_SMDH = "n"
  ) %>%
   sub_missing(
    columns = everything(),
    missing_text = ""
  ) %>%
  opt_table_outline() %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 12,
    table.border.top.width = px(2),
    column_labels.font.weight = "medium",
    row_group.font.weight = "bold"
  )   %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_lnRR),
      rows = p_value_lnRR < 0.05
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_SMDH),
      rows = p_value_SMDH < 0.05
    )
  )%>%
  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
  tab_style(
    style = cell_text(whitespace = "nowrap"),
    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
  )

# saving the image
gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))

# #saving as a docx file or html
# gtsave(RoB_table,here::here("tables/SA_RoB_table.docx"))
# gtsave(RoB_table,here::here("tables/SA_RoB_table.html"))
```

## Table: Sensitivity Analysis: Without Non-aromatic Vs. Aromatic

```{r}
# Loading intercept-only model without Non-aromatic Vs. Aromatic
SA_lnRR_no_comp1<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_comp1.rds"))
SA_SMDH_no_comp1<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_comp1.rds"))

# Loading models for hypothesis without Non-aromatic Vs. Aromatic
lnRR_hypothesis_no_comp1<-readRDS(here::here("model/lnRR_hypothesis_no_comp1.rds"))
SMDH_hypothesis_no_comp1<-readRDS(here::here("model/lnRR_hypothesis_no_comp1.rds"))

# Loading models for design without Non-aromatic Vs. Aromatic
lnRR_design_no_comp1<-readRDS(here::here("model/lnRR_design_no_comp1.rds"))
SMDH_design_no_comp1<-readRDS(here::here("model/lnRR_design_no_comp1.rds"))

**For intercept-only model**

```{r}
SA_intercept_no_comp1 <- tibble::tibble(
  effect_size = c("lnRR",
                  "SMD(H)"),
  data_used = c("Without Non-Aromatic Vs. Aromatic material","Without Non-Aromatic Vs. Aromatic material"),

  Estimate = c(SA_lnRR_no_comp1$b[1],SA_SMDH_no_comp1$b[1]),
  CI_Lower = c(SA_lnRR_no_comp1$ci.lb,
               SA_SMDH_no_comp1$ci.lb),
  CI_Upper = c(SA_lnRR_no_comp1$ci.ub,
               SA_SMDH_no_comp1$ci.ub),
  PI_Lower = c(predict(SA_lnRR_no_comp1)$pi.lb,
               predict(SA_SMDH_no_comp1)$pi.lb),
  PI_Upper = c(predict(SA_lnRR_no_comp1)$pi.ub,
               predict(SA_SMDH_no_comp1)$pi.ub),
  P_value =  c(SA_lnRR_no_comp1$pval,
               SA_SMDH_no_comp1$pval),
  Q_value = c(SA_lnRR_no_comp1$QE,
               SA_SMDH_no_comp1$QE),
  k_effect_sizes = c(SA_lnRR_no_comp1$k,
               SA_SMDH_no_comp1$k),
  n_studies = c(length(SA_lnRR_no_comp1$s.levels.f[[1]]),
               length(SA_SMDH_no_comp1$s.levels.f[[1]])))

# Combine CI and PI into a single column each for compactness
SA_intercept_no_comp1 <- SA_intercept_no_comp1 %>%
  mutate(
    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
    P_value = scales::pvalue(P_value),
    Q_value = sprintf("%.2f", Q_value)
  ) %>%
  select(
    effect_size,
    data_used,
    Estimate,
    CI,
    PI,
    P_value,
    k_effect_sizes,
    n_studies
  )

# Let's make this table pretty
SA_intercept_no_comp1<-SA_intercept_no_comp1%>%
  gt()%>%
  tab_options(
    table.font.size = px(12),
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    heading.title.font.size = px(14),
    heading.subtitle.font.size = px(12),
    column_labels.font.weight = "bold"
  ) %>%
  tab_header(
    title = md("**Summary of Sensitivity Analyses without Non-aromatic Vs. Aromatic experimental design for lnRR and SMD(H) Intercept-only models**")
  ) %>%
  cols_label(
    effect_size = "Effect Size",
    data_used = "Data used in model",
    Estimate = "Estimate",
    CI = "95% CI",
    PI = "95% PI",
    P_value = "P-value",
    k_effect_sizes = "k (No. of Effect Sizes)",
    n_studies = "n (No. of Studies)"
  ) %>%
  fmt_number(
    columns = c(Estimate),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 14,
    table.border.top.width = px(2),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  opt_table_outline()

# Saving as an image
gtsave(SA_intercept_no_comp1, here::here("tables/SA_intercept_no_comp1.png"))
```

**For meta-regressions**

```{r}
pacman::p_load(gt, tidyverse, metafor, purrr, stringr)

## For lnRR Values
lnRR_no_comp1 <- extractor_metareg(lnRR_hypothesis_no_comp1,"Hypothesis")%>%
  bind_rows(extractor_metareg(lnRR_design_no_comp1,"comparision_type"))%>%
  mutate(effect_size = "lnRR")

## For SMDH Values
SMDH_no_comp1 <- extractor_metareg(SMDH_hypothesis_no_comp1,"Hypothesis")%>%
  bind_rows(extractor_metareg(SMDH_design_no_comp1,"comparision_type"))%>%
  mutate(effect_size = "SMDH")

combined_results_no_comp1 <- bind_rows(lnRR_no_comp1, SMDH_no_comp1)%>%
  pivot_wider(
    id_cols = c(moderator, level),
    names_from = effect_size,
    values_from = c(estimate, p_value, CI, PI, k, n),
    names_glue = "{.value}_{effect_size}"
  )%>% # Prepare row labels to mimic grouping
  arrange(moderator, level)%>%
  mutate(row_type = "level")

# Final combined table with headers and levels
 combined_results_no_comp1 <- combined_results_no_comp1 %>%
   # bind_rows(moderator_header ,combined_results) %>%
  arrange(moderator, row_type)%>% select(-row_type)%>%
  relocate(level, .after = moderator)%>%
  mutate(moderator = case_when(
    moderator == "Hypothesis" ~ "1. Hypothesis",
    moderator == "comparision_type" ~ "2. Experimental Design"
  ))%>%mutate(moderator = factor(
    moderator,
    levels = c(
      "1. Hypothesis",
      "2. Experimental Design"
    )
  ))%>%
  arrange(moderator)%>%
   mutate(level = case_when(level==2 ~ "No added material\nvs. Aromatic",
                           level==3 ~ "No added material\nvs. Non-aromatic", .default=level))

# Clean up or reorder columns for display
# Select and order columns for clarity
combined_results_no_comp1 <- combined_results_no_comp1 %>%
  gt(groupname_col = "moderator") %>%
  tab_header(title = md("**Sensitivity Analysis: Multilevel Meta Regressions without Non-aromatic Vs. Aromatic experimental design**")) %>%
  cols_label(
    # R2_marginal_lnRR = "R²_mar",
    # R2_marginal_SMDH = "R²_mar",
    level = "Level",
    estimate_lnRR = "Estimate",
    CI_lnRR = "95% CI",
    PI_lnRR = "95% PI",
    p_value_lnRR = "P-val",
    k_lnRR = "k",
    n_lnRR = "n",
    estimate_SMDH = "Estimate",
    CI_SMDH = "95% CI",
    PI_SMDH = "95% PI",
    p_value_SMDH = "P-val",
    k_SMDH = "k",
    n_SMDH = "n"
  ) %>%
   sub_missing(
    columns = everything(),
    missing_text = ""
  ) %>%
  opt_table_outline() %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 12,
    table.border.top.width = px(2),
    column_labels.font.weight = "medium",
    row_group.font.weight = "bold"
  )   %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_lnRR),
      rows = p_value_lnRR < 0.05
    )
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(p_value_SMDH),
      rows = p_value_SMDH < 0.05
    )
  )%>%
  tab_spanner(label = "lnRR", columns = contains("_lnRR")) %>%
  tab_spanner(label = "SMDH", columns = contains("_SMDH"))  %>%
  tab_style(
    style = cell_text(whitespace = "nowrap"),
    locations = cells_body(columns = c(CI_lnRR, PI_lnRR, CI_SMDH, PI_SMDH))
  )

# saving the image
gtsave(RoB_table,here::here("tables/SA_RoB_table.png"))

@@

```{r}
pacman::p_load(gt, tidyverse, metafor, purrr, stringr)
